The ChEMBL database as Linked Open Data

### 2012-04-18 article.tex
make it clear that there is (or will be soon) a WAR file available for download from GitHub
Added screenshot for Bioclipse-DS.

The Linked Data server used by Bio2RDF has been reconfigured for ChEMBL to provide URL
based services for standard URI resolution, along with text and link searches~\cite{Ansell2011}. 
The configuration files along with build scripts for the ChEMBL-RDF Linked Data server are available on GitHub~\cite{WebAppGitHub}. 
It proxies the standard ChEMBL-RDF URIs by translating URLs between those requested by users and the URIs that are available
in SPARQL endpoints. For example, if the ChEMBL web application is running on the users
local machine, e.g. \url{http://localhost:8080/chembl/}, then a request for the
article with identifier ``a31863'', \url{http://localhost:8080/-chembl/article/a31863},
will be resolved from the database using the full original URI,
\url{http://data.kasabi.com/-dataset/chembl-rdf/13/activity/a31863}. If the
user requested an RDF document using content negotiation, the original URIs will be unchanged,
however, if the user requested an HTML document, the results will contain both the
original RDF triples, represented using RDFa, with links that resolve using the users local machine.

@@

\subsection{Decision Support}

@@

Bioclipse Decision Support (Bioclipse DS)~\cite{Spjuth:2011uq} is a user-oriented tool for 
providing on-time and on-demand information on chemical structures, based on the Bioclipse 
workbench. Such information can include calculated properties, data from database queries, 
and results from predictive models. Bioclipse DS has previously been demonstrated on predictive 
modeling in drug safety assessment~\cite{Spjuth:2011uq} and also been linked to invoke and 
present results from distributed toxicity predictions from the OpenTox infrastructure~\cite{Willighagen:2011kx}.

In this study we extended Bioclipse DS with remote access to ChEMBL-RDF and Chemspider. 
This enables users browsing chemical structures in Bioclipse to look up near neighbors on Chemspider 
via the Chemspider Web API (SOAP) and query ChEMBL-RDF for properties regarding any measured interactions. 
The results are presented alongside predictive models in Bioclipse, and can be used as 
decision support when evaluating chemical structures and consider strategies for optimization.

[TODO: SCREENSHOT from Bioclipse-DS-ChEMBL-RDF]

>>>>

The Linked Data server used by Bio2RDF has been reconfigured for ChEMBL to provide URL
based services for standard URI resolution, along with text and link searches~\cite{Ansell2011}. 
A Java Web Archive (WAR) file along with the configuration files and build scripts for the ChEMBL-RDF Linked Data server are available on GitHub~\cite{WebAppGitHub}. 
It proxies the standard ChEMBL-RDF URIs by translating URLs between those requested by users and the URIs that are available
in SPARQL endpoints. For example, if the ChEMBL web application is running on the users
local machine, e.g. \url{http://localhost:8080/chembl/}, then a request for the
article with identifier ``a31863'', \url{http://localhost:8080/-chembl/article/a31863},
will be resolved from the database using the full original URI,
\url{http://data.kasabi.com/-dataset/chembl-rdf/13/activity/a31863}. If the
user requested an RDF document using content negotiation, the original URIs will be unchanged,
however, if the user requested an HTML document, the results will contain both the
original RDF triples, represented using RDFa, with links that resolve using the users local machine.

@@

\subsection{Bioclipse Decision Support}

@@

Bioclipse Decision Support (Bioclipse DS)~\cite{Spjuth:2011uq} is a user-oriented tool based on the Bioclipse 
workbench for providing on-time and on-demand information on chemical structures. 
Such information can include calculated properties, data from database queries, 
and results from predictive models. Bioclipse DS has previously been demonstrated on predictive 
modeling in drug safety assessment~\cite{Spjuth:2011uq} and also been linked to invoke and 
present results from distributed toxicity predictions from the OpenTox infrastructure~\cite{Willighagen:2011kx}.

In this study we extended Bioclipse DS with remote access to ChEMBL-RDF and Chemspider. 
This enables users browsing chemical structures in Bioclipse to look up near neighbors in Chemspider 
via the Chemspider Web API (SOAP), and for the found compounds to query ChEMBL-RDF for 
available interaction data. The results are presented alongside predictive models in Bioclipse (see Fig \ref{fig:bioclipse-ds}, and can be used for decision support when evaluating chemical structures and consider 
strategies for optimization.

\begin{figure*}[!ht]
		\begin{center}
		\includegraphics[width=16cm]{bioclipse-ds.png}
		\newline
		\caption[wee]{Screnshot from Bioclipse Decision Support with results from a Chsmpider + ChEMBL-RDF search. The top middle canvas contains the query structure, the top right canvas shows the near neighbors in Chemspider (via a similarStructure search), the lower right shows the chemical structure for the selected compound in the top right canvas, and the lower center canvas shows the found interactions for this compound.}
	\label{fig:bioclipse-ds}
		\end{center}
\end{figure*}
